Process-based phenotypes: an application to the Cellular Phenotype Ontology

### 2011-11-21 paper/drinking.tex
edited affiliation

\author[Hoehndorf et al.]{Robert Hoehndorf$^1$ and Gabriella
  Rustici$^2$ and Midori Harris(?)$^3$ and Georgios V. Gkoutos$^{1}$}

\address{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$EBI, Wellcome Trust Genome Campus, Hinxton, Cambridge,
  Cambridge CB2 3EH, UK}

>>>>

\author[Hoehndorf et al.]{Robert Hoehndorf$^1$ and Gabriella
  Rustici$^2$ and Midori A. Harris$^3$ and Georgios V. Gkoutos$^{1}$}

\address{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$EBI, Wellcome Trust Genome Campus, Hinxton, Cambridge,
  Cambridge CB10 1SD, UK\\
  $^{3}$Department of Biochemistry; University of Cambridge, 80 Tennis Court Road, Cambridge CB2 1GA, UK}
